{\itshape Advanced Robotics} A simple path optimization method for motion planning

### 2015-09-30 paper.tex
Fix image and algo-lines references

\begin{figure}[H]
	\centering
	\includegraphics[height=4.9cm,width=1.8cm]{pr2_initial_final_vertical.png}
	\includegraphics[width=5.7cm]{p0_pr2_alone_merged3.png}
	\includegraphics[height=4.9cm]{p1RS_pr2_alone_merged3.png}
	\includegraphics[height=4.9cm]{p1GB_pr2_alone_merged3.png}\\
	\caption{In this motion planning problem, PR2 robot has just to 
exchange the positions of its arms. The task is simple, however, in absence of 
explicit indication, any probabilistic motion planner will compute a path that 
makes the PR2 mobile basis purposelessly moving. This is the case of RRT-connect 
algorithm (left). Path optimization is expected to remove unnecessary motions. 
The popular random shortcut algorithm fails in this case (middle). Our algorithm 
succeeds (right).}
	\label{pr2-final}
\end{figure}

@@

\begin{algorithm}
\begin{algorithmic}[1] % line numerotation
\Procedure{Optimize}{$\xx_0$}
	\State $\alpha \gets \alpha_{init}$; $\epsilon \gets 10^{-3}$
	\State $minReached \gets false$
	\State $validConstraints \gets true$
	\While{($\textbf{not}(noCollision \textbf{ and } minReached)$)}
		\State $\p = \texttt{computeIterate}()$
		\State $minReached = (||\p||<\epsilon \textbf{ or } \alpha=1)$\label{algo:minReached}
		\State $\xx_1 \gets \xx_0 + \alpha\,\p$
		\If{($\alpha \neq 1$)}
			%\State \texttt{solveConstraints($\xx_1$)}
			\If{(\textbf{not}(\texttt{solveConstraints($\xx_1$)}))} \label{algo:solveCons}
				\State $\alpha \gets \alpha*0.5$
				\State $validConstraints \gets false$\label{algo:solveCons2}
			\Else
				\State $validConstraints \gets true$
			\EndIf
		\EndIf
		\If{(\textbf{not}(\texttt{validatePath($\xx_1$)}))}
			\State $noCollision \gets false$
			\If{$(\alpha \neq 1)$}
				\State \texttt{addCollisionConstraints}()\label{algo:addCons}
				\State $\alpha \gets 1$
			\Else
				\If{($validConstraints$)}\label{algo:towardMin}
					\State $\alpha \gets \alpha_{init}$\label{algo:towardMin2}
				\EndIf
			\EndIf
		\Else
			\State $\xx_0 \gets \xx_1$
			\State $noCollision \gets true$\label{algo:noCollision}
			\State $\alpha \gets 0.5*(1+\alpha)$
		\EndIf
	\EndWhile
	\Return $\xx_0$
\EndProcedure
\end{algorithmic}
\caption{Gradient-based path-optimization.} \label{algo:gradient}
\end{algorithm}

Each time a collision-constraint is added, 
the solution of the current QP is tested (i.e. $\alpha = 1$). If this path is collision-free, the algorithm returns it as the solution (lines~\ref{algo:minReached}-\ref{algo:noCollision}). Otherwise, 
smaller steps are iteratively applied and tested toward the minimum (lines~\ref{algo:towardMin}-\ref{algo:towardMin2}), and constraints are added each time a collision is found (line~\ref{algo:addCons}).

If the constraint relinearization fails to validate Property~\ref{prop:collision free}, $\alpha$ is halved and the algorithm restarts from the latest valid path (lines~\ref{algo:solveCons}-\ref{algo:solveCons2}).

@@

>>>>

@@

\begin{algorithm}
\begin{algorithmic}%[1] % line numerotation
\Procedure{Optimize}{$\xx_0$}
	\State $\alpha \gets \alpha_{init}$
	\State $minReached \gets false$
	\While{($\textbf{not}(noCollision \textbf{ and } minReached)$)}
		\State $\p = \texttt{computeIterate}()$
		\State $minReached = (||\p||<10^{-3} \textbf{ or } \alpha=1)$
		\State $\xx_1 \gets \xx_0 + \alpha\,\p$
		\If{(\textbf{not}(\texttt{validatePath($\xx_1$)}))}
			\State $noCollision \gets false$
			\If{$(\alpha \neq 1)$}
				\State \texttt{addCollisionConstraints}()
				\State $\alpha \gets 1$
			\Else
				\State $\alpha \gets \alpha_{init}$
			\EndIf
		\Else
			\State $\xx_0 \gets \xx_1$
			\State $noCollision \gets true$
		\EndIf
	\EndWhile
	\Return $\xx_0$
\EndProcedure
\end{algorithmic}
\caption{Gradient-based path-optimization.} \label{algo:gradient}
\end{algorithm}

Each time a collision-constraint is added, 
the solution of the current QP is tested (i.e. $\alpha = 1$). If this path is collision-free, the algorithm returns it as the solution. Otherwise, 
smaller steps are iteratively applied and tested toward the minimum, and constraints are added each time a collision is found.

If the constraint relinearization fails to validate Property~\ref{prop:collision free}, $\alpha$ is halved and the algorithm restarts from the latest valid path.

@@

\begin{figure}[H]
	\centering
	\includegraphics[height=4.9cm,width=1.8cm]{pr2_initial_final_vertical.png}
	\includegraphics[width=5.7cm]{p0_pr2_alone_merged3.png}
	\includegraphics[height=4.9cm]{p1RS_pr2_alone_merged3.png}
	\includegraphics[height=4.9cm]{p1GB_pr2_alone_merged3.png}\\
	\caption{In this motion planning problem, PR2 robot has just to 
exchange the positions of its arms. The task is simple, however, in absence of 
explicit indication, any probabilistic motion planner will compute a path that 
makes the PR2 mobile basis purposelessly moving. This is the case of RRT-connect 
algorithm (left). Path optimization is expected to remove unnecessary motions. 
The popular random shortcut algorithm fails in this case (middle). Our algorithm 
succeeds (right).}
	\label{pr2_final}
\end{figure}
